Rising from the Ashes: How the Milky Way Got Its Scars

### 2024-04-30 paper/src/res.tex
Add surfdens movie plot

\section{Results}\label{sec:results}
\subsection{Abundance Distribution}\label{ssec:abundplane}
In Figure~\ref{fig:fig1}, briefly discussed in Section~\ref{sec:intro}, we show the abundance distribution of the Milky Way as well as two of our idealized merger simulations in the upper panels. A number of our idealized simulations exhibit either a bimodal or unimodal abundance distribution, and so we have selected two representative examples. In detail, the simulation labeled bimodal had orbital parameters of $R_0=142\,\kpc$, $V_0=116\,\kms$, and $\eta=0.4$. The unimodal simulation is identical, except that $R_0=129\,\kpc$.

>>>>

\section{Results}\label{sec:results}
\subsection{Surface Density Projections}\label{ssec:projections}
Before dissecting the simulated galaxies in detail, we first take a look at the surface density projections of the gas and stars in the central region, situated on the central galaxy. This is shown in Figure~\ref{fig:projections}. In each grouping of four, the bottom and top rows show the face-on and edge-on views, respectively. The left and right columns show the gas and stellar surface density. Each panel is oriented with respect to the stellar angular momentum of the final snapshot ($t=8\,\Gyr$). The angular momentum is computed using all star particles within the half-mass radius.

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{surfdens.pdf}
  \caption{The surface density projections of the gas and stars over time of the idealized merger simulation with $R_0=142\,\kpc$, $V_0=116\,\kms$, and $\eta=0.4$ (i.e., the ``bimodal'' simulation). Every panel is oriented with respect to the final ($t=8\,\Gyr$) snapshot. In each grouping of four, the lower and upper rows show the face-on and edge-on projections, respectively. The left and right columns show the gas and stellar surface densities, respectively. The side-length of each panel is $30\,\kpc$, and the image is a projection through a box with the same side-length. \red{Need to fix spacing between panels and add scale bar.}}
  \label{fig:projections}
\end{figure*}

\subsection{Abundance Distribution}\label{ssec:abundplane}
In Figure~\ref{fig:fig1}, briefly discussed in Section~\ref{sec:intro}, we show the abundance distribution of the Milky Way as well as two of our idealized merger simulations in the upper panels. A number of our idealized simulations exhibit either a bimodal or unimodal abundance distribution, and so we have selected two representative examples. The simulation labeled bimodal had orbital parameters of $R_0=142\,\kpc$, $V_0=116\,\kms$, and $\eta=0.4$. The unimodal simulation is identical, except that $R_0=129\,\kpc$.
